%%
\ifexam
	\part[2]
	\else
	\question[1]
\fi
%Begin Question----------------------------------------------------
\emph{Fill-in-the-blank:} Of the materials provided on the graph in Fig. \ref{fig:StiffInsulate}, \fillin[bamboo] is the best choice if we aim to \emph{maximize} the materials index $M = \frac{E^{\frac{1}{2}}}{k}$. 

Show work on the graph if you hope for partial credit.

%FileID-------------------------------------------------
\begin{FileID}
	\begin{center}
		\begin{tabular}{cc}
			\hline
			\hline
			\#FileTag:C21-MC-Q2-2b.tex & 	\#SourceTag:Original\\ %change
			\#AuthorTag:JDEmery & \#UseTag:QuizExam\\ %change
			\hline
			\#AssignmentTag:QuizL10-2 & \#TermTag:W17 \\ %add
			\hline
			\#TopicTag:Semiconductivity & \#TopicTag:OpticalTransmission\\ %change
			\hline
			\#TypeTag:MultipleChoice & \\
			\hline
		\end{tabular}
	\end{center}
\end{FileID}

%Solution-----------------------------------------------------
\begin{solution}

We want to maximize the materials index, $M = \frac{E^{\frac{1}{2}}}{k}$. This means, generally, we want high values of $E$ and low values of $k$, so we'll be in the bottom right-hand corner of the graph.

We use the materials index result from \#2 and find the material that is furthest from that line.

Bamboo is the best option, but paper/cardboard is a \emph{very} close second and I'll accept that as well.
%
\end{solution}

%Rubric------------------------------------------------------------------
\begin{rubric}
	\begin{enumerate}
		\item Getting this question correct is dependent on the result they got for \#2. If they have a slope of 2, they should still know they are maximizing $M = \frac{E^{\frac{1}{2}}}{k}$. In that case. That would be tungsten carbide, by a hair, soda-lime as a close second and also acceptable. If they do that, give them full credit. 
		\item If they go the opposite direction and find flexible polymer foam for a slope of 2, give them 25\%.
		\item If they go opposite direction for a slope of 1/2 and get silver, give 25\%.
	\end{enumerate}
\end{rubric}

%Outcomes--------------------------------------------------
\begin{outcomes}
They often select something above the line, like silver or copper.

	\begin{center}
		\begin{tabular}{ccc|ccc}
			\hline\hline
			Class-Term Used & Term Instructor & Assessment & Full Credit & Partial Credit & No Credit\\
			\hline
			201-W16 & Emery & QuizL10-2 & 50\% & 30\% & 20\%\\    %change			\hline
		\end{tabular}
	\end{center}
\end{outcomes}

%Comments-------------------------------------------------------------------
\begin{comments}

Paired with Ashby-MC-2-2. Need more of these!

\end{comments}